---
title: "p8105_hw5_as6447"
author: "Armaan Sodhi"
date: "2022-11-11"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```
## Problem 1

The code chunk below imports the data in individual spreadsheets contained in `./data/zip_data/`. To do this, I create a dataframe that includes the list of all files in that directory and the complete path to each file. As a next step, I `map` over paths and import data using the `read_csv` function. Finally, I `unnest` the result of `map`.

```{r}
full_df = 
  tibble(
    files = list.files("data/zip_data/"),
    path = str_c("data/zip_data/", files)
  ) %>% 
  mutate(data = map(path, read_csv)) %>% 
  unnest()
```

The result of the previous code chunk isn't tidy -- data are wide rather than long, and some important variables are included as parts of others. The code chunk below tides the data using string manipulations on the file, converting from wide to long, and selecting relevant variables. 

```{r}
tidy_df = 
  full_df %>% 
  mutate(
    files = str_replace(files, ".csv", ""),
    group = str_sub(files, 1, 3)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome",
    names_prefix = "week_") %>% 
  mutate(week = as.numeric(week)) %>% 
  select(group, subj = files, week, outcome)
```

Finally, the code chunk below creates a plot showing individual data, faceted by group. 

```{r}
tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subj, color = group)) + 
  geom_point() + 
  geom_path() + 
  facet_grid(~group)%>%
```

This plot suggests high within-subject correlation -- subjects who start above average end up above average, and those that start below average end up below average. Subjects in the control group generally don't change over time, but those in the experiment group increase their outcome in a roughly linear way. 

## Problem 2

1.Describe the raw data. 

2.Create a city_state variable (e.g. “Baltimore, MD”) and then summarize within cities to obtain the `total number of homicides` and` the number of unsolved homicides` (those for which the disposition is “Closed without arrest” or “Open/No arrest”).
```{r}
homicide_data = read.csv('data/homicide-data.csv')%>% 
   janitor::clean_names()%>%
   unite('city_state',city:state,remove=FALSE, sep = ', ')%>%
      unite('Victim_full_name',victim_first:victim_last,remove=FALSE, sep = ' ')%>%
   select(-city,-state,-victim_last,-victim_first)%>%
   rename(longitude=lon, latitude=lat)%>%
   mutate(
      unsolved_murder = if_else(disposition %in% c("Closed without arrest","Open/No arrest"),1, 0),
       city_state = replace(city_state, city_state %in% 'Tulsa,AL','Tulsa,OK')
      )
  
```

```{r}
homicide_data1=
homicide_data%>%
   group_by(city_state)%>%
   summarize(
      total_number_homicides=n(),
      number_unsolved_murders = sum(unsolved_murder))
```


2.For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; 
   a.save the output of prop.test as an R object
   b.apply the broom::tidy to this object
   c.pull the estimated proportion and confidence intervals from the resulting tidy       dataframe.
```{r}
baltimore_data= 
   homicide_data1%>%
   filter(city_state %in% 'Baltimore, MD')%>%
   mutate(p_test = 
             map2(number_unsolved_murders,total_number_homicides, ~prop.test(.x,.y )%>%
                     broom::tidy()))%>%unnest()
baltimore_data%>%
   select(city_state,estimate,'CI_lower'=conf.low, 'CI_upper'=conf.high)

   prop_test=prop.test(
      x = baltimore_data%>% pull('number_unsolved_murders'),
      n = baltimore_data%>% pull('total_number_homicides'),
      alternative = c("two.sided"),
      conf.level = 0.95, correct = TRUE)


    
```

3.Now run prop.test for each of the cities in your dataset, and 
   a.extract both the proportion of unsolved homicides and the confidence interval for     each. 
   b.Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list
   columns and unnest as necessary to create a tidy dataframe with estimate proportions    and CIs for each city.
```{r}
homicide_cities= 
   homicide_data1%>%
   mutate(p_test = 
             map2(
                number_unsolved_murders,total_number_homicides, ~prop.test(.x,.y )%>%
                     broom::tidy()))%>%unnest()
homicide_cities%>%
   select(city_state,estimate,'CI_lower'=conf.low, 'CI_upper'=conf.high)
```

4.Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides

```{r}

```

## Problem 3

In this problem, you will conduct a simulation to explore power in a one-sample t-test.

1.First set the following design elements:

Fix n=30
Fix σ=5
Set μ=0. Generate 5000 datasets from the model

x∼Normal[μ,σ]

```{r}

```

2.For each dataset, save μ^ and the p-value arising from a test of H:μ=0 using α=0.05. Hint: to obtain the estimate and p-value, use broom::tidy to clean the output of t.test.
```{r}

```

3.Repeat the above for μ={1,2,3,4,5,6}, and complete the following:
```{r}

```

4.Make a plot showing the proportion of times the null was rejected (the power of the test) on the y axis and the true value of μ on the x axis. Describe the association between effect size and power.
```{r}

```

5.Make a plot showing the average estimate of μ^ on the y axis and the true value of μ on the x axis. Make a second plot (or overlay on the first) the average estimate of μ^ only in samples for which the null was rejected on the y axis and the true value of μ on the x axis. 
```{r}

```

6.Is the sample average of μ^ across tests for which the null is rejected approximately equal to the true value of μ? Why or why not?
Extra topics survey
```{r}

```

